---
title: Data description
---

```{r}
#| include: false
library(tidyverse)
```

The following is generated from the field_descriptions table which is included
in the database which can be [downloaded here](rw.db), or you can download a zip
file with csvs [here](rw_csvs.zip).

First, get table as a dataframe.

```{r}
con <- DBI::dbConnect(RSQLite::SQLite(), "../data/rw.db")
DBI::dbListTables(con)
descriptions <- tbl(con, "field_descriptions") |> collect()
```

The field (column) descriptions are printed out by table below. The
abbreviations PK and FK are for primary key and foreign key, respectively. The
primary key serves as the unique identifier for records (rows) in the table. A
foreign key refers to a column in another table, which should be used for join
operations. If a table has no PK listed, then its PK is a hidden column called
rowid.

```{r}
#| code-fold: true
print_desctiption <- function(table_name) {
  cat("\n\n## `", table_name, "`\n\n", sep = "")
  filter(descriptions, table == table_name) |>
    select(-table) |>
    knitr::kable() |>
    print()
}
```

```{r}
#| output: asis
walk(unique(descriptions$table), ~ print_desctiption(.x))
```
